## Distractor analysis with dexter

```{r}
#| label: setup
#| include: false
rm(list=ls())
library(tidyverse)
library(dexter)
# load in the dataset
responses <- read_csv('data/responses.csv')
keys <- read_csv('data/key.csv')
```

```{r}
# Create the rules
rules <- keys_to_rules(keys, include_NA_rule = TRUE)
db <- start_new_project(rules, db_name = ":memory:", person_properties=list(gender="unknown"))
```

```{r}
add_booklet(db, responses, "y7") 
get_booklets(db)
head(get_items(db))
get_persons(db) %>% 
  glimpse()
tt = tia_tables(db)
tt$booklets
tt$items

# Look at distractor plots for all items
n_items <- nrow(keys)
for(i in 1:n_items){
  distractor_plot(db, keys$item_id[i])
}
```

## Analysis questions
Does the slope of the correct answer always rise from left to right? 
Does the curve for the correct answer always rise above those for the incorrect answers?
What does the steepness of the slope for the correct answer tell you about an item?
Change the key so that one of the items is incorrectly marked. What do you see in the distractor analysis?
What is the role of the curtains (the shaded areas in the plots)? Are there any items where they are particularly helpful?
How many distractors generally seem to be useful?
What would you typically expect the probability of guessing the correct answer to be for a MC item with 5 choices? If you look at the point at which the distractors cross the y-axis where sum score = 0, what do you learn about the actual probabilities?
Can you make any recommendations for improvement based on the distractor analysis?


```{r}
close_project(db)
```