# Distractor analysis with dexter

Dexter is an R package for managing and analyzing data from educational tests and other projects involving individual assessment. <https://dexter-psychometrics.github.io/dexter/>

## What does it do?
*    Easily create a data base tailored to the specific structure of test data
*    Safeguard data integrity through a variety of checks; easily recover from wrong answer keys and other human errors
*    Classical test and item analysis
*    Assess the fit of the Rasch / partial credit model through comparison against both the observed data and a more flexible model; identify problematic items
*    Calibrate the test with either conditional maximum likelihood (CML) or MCMC methods
*    Estimate ability with CML or MCMC methods, produce conversion tables, draw plausible values
*    Apply a variety of mostly novel methods for DIF analysis, equating pass/fail limits and more.

Dexter fundamentals: <https://dexter-psychometrics.github.io/dexter/articles/dexter.html>

Dexter blog: <https://dexter-psychometrics.github.io/dexter/articles/blog/index.html>


```{r}
#| label: setup
#| include: true
#| echo: true
#| output: false
#| warning: false
rm(list=ls())
library(tidyverse)
library(dexter)
# load in the dataset
responses <- read_csv('data/responses.csv')
keys <- read_csv('data/key.csv')
# Create the rules
rules <- keys_to_rules(keys, include_NA_rule = TRUE)
db <- start_new_project(rules, db_name = ":memory:", person_properties=list(gender="unknown"))
add_booklet(db, responses, "y7") 
```

```{r}

get_booklets(db)
head(get_items(db))
get_persons(db) %>% 
  glimpse()
tt = tia_tables(db)
tt$booklets
knitr::kable(tt$items, digits = 2)

```

## Distractor plots
Distractor plots provide visual information at response level. This is a non-parametric regression of the probability of each response (including non-response) on the total score, particularly useful to detect issues with multiple choice items due to wrong keys or, simply, sub-optimal item writing. 

```{r}
#| warning: false
# Look at distractor plots for all items
n_items <- nrow(keys)
for(i in 1:n_items){
  distractor_plot(db, keys$item_id[i])
}
```

## Analysis questions
1. Does the slope of the correct answer always rise from left to right? 
2. Does the curve for the correct answer always rise above those for the incorrect answers?
3. What does the steepness of the slope for the correct answer tell you about an item?
4. Change the key so that one of the items is incorrectly marked. What do you see in the distractor analysis?
5. What is the role of the curtains (the shaded areas in the plots)? Are there any items where they are particularly helpful?
6. How many distractors generally seem to be useful?
7. What would you typically expect the probability of guessing the correct answer to be for a MC item with 5 choices? If you look at the point at which the distractors cross the y-axis where sum score = 0, what do you learn about the actual probabilities?
8. Can you make any recommendations for improvement based on the distractor analysis?


```{r}
close_project(db)
```