# Correlations

## Item Total Correlations

Item total correlations, are generally used as supporting evidence for the reliability of test forms. Items may be excluded from a test form if they have a poor correlation to the total score. The item total correlation is the correlation between the item score and the total score.

```{r}
#| label: setup
#| include: true
#| warning: false

rm(list=ls())
library(tidyverse)
# load in the dataset
responses <- read_csv('data/responses.csv')

# sum across the columns with _score_ in the name and add to a new column called total.
# make sure to ignore missing values
# https://dplyr.tidyverse.org/articles/rowwise.html
# https://dplyr.tidyverse.org/reference/pick.html?q=pick#ref-usage
responses <- responses %>% mutate(total = rowSums(pick(ends_with("_score")), na.rm = TRUE))
```
```{r}
#| label: tbl-itemr
#| tbl-cap: Item Total Correlations
# correlate each item score with the total score
# note that this function includes the studied item score in the total score for simplicity, but normally the item score would be excluded from the total score, see https://personality-project.org/r/html/alpha.html
item_total_r <- responses %>% 
  select(ends_with("_score")) %>% 
  mutate(total = responses$total) %>% 
  gather(key = "item", value = "score", -total) %>% 
  mutate(item = str_remove(item, "_score")) %>% 
  group_by(item) %>% 
  summarise(mean = mean(score, na.rm=T), correlation = cor(score, total, use = "pairwise.complete.obs")) %>% 
  arrange(desc(correlation))
  
knitr::kable(item_total_r, digits = 2)
```

## Discussion
Is there a relationship between item difficulty and item total correlation? 
Can you plot this relationship?
Can you see any issues with excluding items based on item total correlation?

## Inter-item Correlations
```{r}
#| label: inter-item-r
#| include: true
# Correlate each item score with every other item score
# https://corrr.tidymodels.org/
library(corrr)
x1 <- responses %>% 
  select(ends_with("_score")) %>%
  correlate() %>% 
  rearrange() %>%
  shave()

fashion(x1)

stretch(x1, na.rm = TRUE) %>% arrange(r)

```

## Try some visulations suggested by the package eg. the network plot
```{r}
#| label: network-plot
#| include: true
#| fig-cap: Network diagram of inter-item correlations
x2 <- responses %>% 
  select(ends_with("_score")) %>%
  correlate()
x2 %>% network_plot(min_cor = .1)
```

