# Item Discrimination
The more an item discriminates among individuals with different amounts of the underlying concept of interest, the higher the discrimination index.

```{r}
#| label: setup
#| include: false
rm(list=ls())
library(tidyverse)
# load in the dataset
responses <- read_csv('data/responses.csv')
```

## The extreme group method (@cappelleri)
### Step 1
Partition respondents who have the highest and lowest overall scores on the overall scale, aggregated across all items, into upper and lower groups. The upper group can be composed of the top x% (e.g., 25%) of scores on the scale, while the lower group can be composed of the bottom x% (e.g., 25%) of scores on the scale.

```{r}
# calculate the total score for each respondent
responses <- responses %>% 
  mutate(total = rowSums(pick(ends_with('_score')),na.rm=TRUE)) 

# partition the respondents into 4 quartiles based on their total score
responses <- responses %>% 
  mutate(quartile = cut(total,quantile(total,probs=c(0,0.25,0.5,0.75,1)),labels=c('Q1','Q2','Q3','Q4'),include.lowest=TRUE))

# double check
responses %>% 
  group_by(quartile) %>% 
  summarise(mean_score = mean(total))

items <- responses %>% select(quartile, ends_with('_score'))
# pivot the items longer for analysis
items <- items %>% pivot_longer(-quartile, names_to = 'item', values_to = 'score')
```

### Step 2
Examine each item and determine the proportion of individual respondents in the sample who correctly respond to each item in the upper group and lower group.

```{r}
# create a summary table with item stats
item_stats <- items %>% 
  group_by(quartile, item) %>%
  summarise(mean_score = mean(score, na.rm=TRUE))
# pivot wider so we have the item stats for each quartile
item_wide_stats <- item_stats %>% 
  pivot_wider(names_from = quartile, values_from = mean_score)

item_wide_stats <- item_wide_stats %>% mutate(
    item_name = factor(item, levels=paste('Q',1:20, '_score',sep=''),labels = paste0('Q',1:20),ordered = TRUE)
    ) %>% arrange(item_name) 

item_wide_stats <- item_wide_stats %>% select(
    item_name, 
    Q1 = `Q1`, 
    Q2 = `Q2`, 
    Q3 = `Q3`, 
    Q4 = `Q4`
    )

```

### Step 3
Subtract the pair of proportions noted in Step 2.

```{r}
item_wide_stats <- item_wide_stats %>% mutate(
    Q1_Q4 = Q4 - Q1,
    )
knitr::kable(item_wide_stats, digits=2)
```


## Interpretation
The higher the item discrimination index, the more the item discriminates. For example, if 60% of the upper group and 25% of the lower group endorse a particular item in the scale, the item discrimination index for that item would be calculated as (0.60−0.25) = 0.35.

## Extension Exercise
Try and recreate the item discrimination plot [here](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4096146/)