---
title: "Demographics"
format: html
execute:
  echo: true
---

### Working with demographic data
In our dataset we have the the variable gender. Let's examine what sort of variable gender is.

```{r}
#| label: setup
#| include: false
rm(list=ls())
library(tidyverse)
# load in the dataset
responses <- read_csv('data/responses.csv')
```

```{r}

# What class of variable is gender in the dataset?
print(class(responses$gender))

```

To work with demographic data we need to convert the variable to a factor. We can do this using the factor function.

```{r}
# List all the permutations of gender in the dataset
print(unique(responses$gender))
```

```{r}
responses <- responses %>% 
  mutate_at(vars(gender), factor, levels=c('M','F'),labels=c('Male','Female'))
```

## What are the proportions of Male / Female in the dataset?

```{r}
#| label: proportions
#| include: true
responses %>%
  group_by(gender) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
```

## Remove the missing data for simplicity

```{r}
# Remove the missing data for simplicity
responses <- responses %>% drop_na(gender)
```

## Now go back to the Test Information and produce a table and a histogram by gender
**What do you learn from the grouped information?**
