# Item Difficulty and Person Ability

A more traditional approach to the Rasch model is operationalised in the package TAM[@TAM_4.1-4] <https://alexanderrobitzsch.github.io/TAM/>

## Fitting the Rasch model with TAM

```{r}
#| include: true
#| echo: true
#| output: false
#| warning: false
rm(list=ls())  #remove all variables in the R environment
library(tidyverse)
library(TAM)  #load the package TAM so we can use the functions in TAM

# load in the dataset
responses <- read_csv('data/responses.csv')
# keep the scores
responses <- responses %>% select(ends_with('score'))

#run a joint maximum likelihood estimation of the Rasch model
mod1 <- tam.jml(responses)
```

## Model Summary
All the results of the Rasch analysis are stored in the object called "mod1"
```{r}
#| include: true
#| echo: true
#| output: true
#| warning: false
summary(mod1)  #see a summary of the results
```


## Item Difficulty

Items are assigned a difficulty parameter xsi.ite. The higher the value, the more difficult the item.

```{r}
#| label: tbl-item-difficulty
#| tbl-cap: Item Difficulty
knitr::kable(mod1$item)
```

How would you describe the relationship between the item facility (M) and the item difficulty (xsi.item) ?

```{r}
#| label: fig-M-xsi
#| fig-cap: Item Difficulty compared to Item Means
p <- ggplot(mod1$item, aes(x=M, y=xsi.item))
p <- p + geom_point()
p
```

## Person Ability
Persons are given an estimated ability (theta). Higher theta means more ability.

```{r}
#| label: tbl-person-ability
#| tbl-cap: Person Ability
summary(mod1$theta)
```

How would you describe the relationship between person ability and total score?
```{r}
#| label: fig-ability
#| fig-cap: Total score compared to person ability
person_abilities <- tibble(theta=mod1$theta, sumScore = mod1$PersonScores)
p <- ggplot(person_abilities, aes(x=theta, y= sumScore))
p <- p + geom_point()
p

```

## Item Characteristic Curves
Item characteristic curves are used to examine the fit of the items to the Rasch model. The empirical data in black should follow the modelled data in blue for a good fit. As with *dexter*, items may be either under or over discriminating empirically compared to the model.
```{r}
plot(mod1)
```

## Item person map
Remember, under the Rasch model, person ability and item difficulty are on the same scale. If we plot a histogram of person ability against the location of item difficulty we can directly consider how well items are targeting person ability. The plot is referred to as a Wright map. How well targeted do you think this test is?

```{r}
#| label: fig-wright-map
#| fig-cap: Wright Map
library(WrightMap)
wrightMap(mod1$theta, mod1$xsi, item.side = itemClassic)

```
