# Item Difficulty and Person Ability

## Fitting the Rasch model with TAM

```{r}
#| include: true
#| echo: true
#| output: false
#| warning: false
rm(list=ls())  #remove all variables in the R environment
library(tidyverse)
library(TAM)  #load the package TAM so we can use the functions in TAM

# load in the dataset
responses <- read_csv('data/responses.csv')
# keep the scores
responses <- responses %>% select(ends_with('score'))

#run a joint maximum likelihood estimation of the Rasch model
mod1 <- tam.jml(responses)
```

```{r}
#| include: true
#| echo: true
#| output: true
#| warning: false

#All the results of the Rasch analysis are stored in the object called "mod1"
summary(mod1)  #see a summary of the results

#See specific results from the Rasch analysis
knitr::kable(mod1$item)
head(mod1$WLE)
mod1$WLEreliability
```

## Item and person summary statistics
```{r}
summary(mod1$item1)
summary(mod1$WLE)

person_abilities <- tibble(theta=mod1$WLE)
p <- ggplot(person_abilities, aes(x=theta))
p <- p + geom_histogram(binwidth = 0.5)
p

```

## Item Characteristic Curves
```{r}
plot(mod1)
```

## Item person map
```{r}
library(WrightMap)
wrightMap(mod1$WLE, mod1$xsi, item.side = itemClassic)

```


## Exercises
1. Compare IRT estimated item difficulties with CTT item scores.
2. Use the R function cor to calculate correlation. Use plot to show the relationship graphically.
3. Compare IRT reliability and CTT reliability
4. Visually compare ‘steepness’ of IRT observed ICC with CTT point-biserial correlation.
5. Compare students’ IRT ability measures (WLE) with students’ test scores (CTT).
6. Compute correlation and plot the two variables to show the relationship.